Identifying regime transitions for water governance at a basin scale

### 2022-04-26 paper/main/manuscript.tex
feat(introduction,-manuscript): change fig path correctly, add knowledge gap and defination of water governace
BREAKING CHANGE:
docs(manuscript): metadata pasted

\graphicspath{{/Users/songshgeo/Documents/VScode/water_governance_challenges/figures/}}
\begin{document}

\title[Article Title]{Article Title}

@@

\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}

\keywords{keyword1, Keyword2, Keyword3, Keyword4}

>>>>

\graphicspath{{/Users/songshgeo/Documents/Pycharm/WGRegimes_YRB_2020/figures/}}
\begin{document}

\title[Article Title]{Identifying regime transitions for water governance at a basin scale}

@@

\abstract{In many large river basins, water governance for socio-economic development has led to a global transformation of water governance regimes from natural to social-ecological or ‘hydrosocial’ situations. Water governance decides who gets water, when, and how much. Identifying how and when water governance regimes change is therefore critical to understanding social-ecological water dynamics and guiding the efficient and sustainable use of water. We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale. Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China), it describes how water governance shifts between three regimes (massive supply regime; purpose-focused regime; and many-sided governance regime, respectively) over half a century. Our application of the IWGI offers a way to link the shifts of water governance to environmental, economic social and political changes. As a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines on the coordinated governance of big river basins in general.}

\keywords{
    Regime shifts,
    Water use,
    Water governance,
    Transformation,
    Sustainability
}
